Conoco Phillips 2020

### 2020-08-28 Submission/letter.tex
updated letter to the editor; forgot to compile the pdf file, can you do that, sorry

In this manuscript, we  develop a forecasting methodology for providing credible forecasts for time series that are known to  experience a shock in the future. It is a general methodology that has various potential real-life applications in forecasting during  \emph{unprecedented} time. We achieve this by borrowing knowledge from other time series that have undergone similar shocks for which post-shock outcomes are observed. We construct three shock effect estimators  with the aim of minimizing average forecast risk. We propose risk-reduction propositions that provide conditions that establish when our methodology works. Bootstrap and leave-one-out cross validation procedures are provided to prospectively evaluate those conditions and estimate corresponding correctness. We use a real data example of forecasting Conoco Phillips stock price during the time  of   oil price control and COVID-19 pandemicto verify  our methodology.

>>>>

In this manuscript, we  develop forecasting methodology for providing credible forecasts for time series that are known to have undergone a recent shock for which no post-shock data is observed. Our methodology has various potential real-life applications in many forecasting settings.

We construct credible forecasts by borrowing knowledge from other time series that have undergone similar shocks for which post-shock outcomes are observed. We propose risk-reduction propositions that provide conditions that establish when our methodology works. Bootstrap and leave-one-out cross validation procedures are provided to prospectively evaluate the performance of our methodology.

We demonstrate the utility of our methodology with a real data analysis involving the forecasting of Conoco Phillips stock price during a time period of massive oil price volatility and increasing COVID-19 panic. We also provide several numerical examples that demonstrate the effectiveness of our prospective evaluation procedures.
